---
title: "GO.db3: parquet-based AnnotationDbi emulation of GO.db for Gene Ontology"
shorttitle: "Modernizing GO.db in Bioconductor"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{GO.db3: parquet-based AnnotationDbi emulation of GO.db for Gene Ontology}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

This package aims to replace GO.db.  The AnnotationPipeline system in which
GO.db is constructed has become stale.  Instead of SQLite following a complex
schema (apparently built to foster cross-curation of different annotation
resources), we base the package on similarly structured parquet files in which
the `GO:nnnnnnn` tag can be regarded as primary key.

# Demonstration

An object called `GO.db` is an instance of a new S4 class `GOparq`.

A select method is available.
```{r lk,message=FALSE}
library(GO.db3)
GO.db
select(GO.db, keys=c("GO:0009435", "GO:0009436"), keytype="GOID", columns=c("GOID", "TERM", "ONTOLOGY"))
```

The legacy environments are available.

```{r lkenv}
GOTERM
get("GO:0009435", GOTERM)
```
